%% start of file `template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,letter]{moderncv}

% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[grey]{classic}                % idem

% character encoding
           % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Harry J.}
\familyname{Gindi}
\title{Curriculum Vit\ae}               % optional, remove the line if not wanted
\address{23 Charles Ct.}{Ocean, NJ 07712}
\phone{+1 (908) 433-1988}                      % optional, remove the line if not wanted
\email{harry.gindi@gmail.com}                      % optional, remove the line if not wanted
\extrainfo{Date of Birth: November 28, 1989\\Country: United States}
%\photo[64pt]{mug.png}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{"No man should escape our universities without knowing how little he knows." -- J. Robert Oppenheimer}                 % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\section{Education}
\cventry{2008--2014}{BSc in Pure Mathematics}{University of Michigan}{Ann Arbor}{MI}{}

\section{Publications}
\cventry{Preprint}{A homotopy theory of weak \(\omega\)-categories}{}{}{}{arXiv:1207.0860 [math.CT]}

\section{Languages}
\cventry{English}{Fluent}{}{Native speaker}{}{}
\cventry{French}{Partially fluent}{}{Fourth semester proficiency, Experience reading monographs and scholarly works}{}{}

\section{Teaching Experience}
\cventry{Fall 2012}{Introduction to real analysis}{}{}{private tutor}{}
\cventry{Fall 2012}{Linear Algebra}{}{}{private tutor}{}
\cventry{Fall 2011}{Linear algebra}{}{}{tutor for the Kiluk experiment}{}
\cventry{Summer 2011}{Linear Algebra}{}{}{private tutor}{}
\cventry{Fall 2010}{Linear algebra}{}{}{tutor for the Kiluk experiment}{}

\section{Attended Conferences}
\cventry{May 2012}{Derived Algebraic Geometry RTG Learning Workshop}{}{Ann Arbor}{MI}{}
\cventry{Apr 2012}{Midwest Topology Seminar}{}{West Lafayette}{IN}{}
\cventry{Nov 2010}{Midwest Number Theory Conference for Graduate Students}{}{Ann Arbor}{MI}{}
\cventry{Oct 2010}{Midwest Topology Seminar}{}{Detroit}{MI}{}

\section{Selected Mathematics Courses (by subject)}
\cvitem{Fall 2012}{Local langlands correspondence.}
\cvitem{Winter 2012}{Group theory.}
\cvitem{Fall 2011}{Algebraic geometry I.}
\cvitem{Winter 2011}{Representation theory. Topics in commutative algebra. Algebraic topology II.}
\cvitem{Fall 2010}{Lie algebras and their representations. Algebraic number theory. Algebraic topology I.}
\cvitem{Winter 2010}{Honors analysis II. Introduction to algebraic topology. Topics in commutative algebra.}
\cvitem{Fall 2009}{Honors analysis I. Number theory. Commutative algebra.}
\cvitem{Winter 2009}{Honors mathematics II. Introduction to topology.}
\cvitem{Fall 2008}{Honors mathematics I.}

\end{document}